Model Search in Relational Domains

### 2016-10-22 algorithm.tex
section 5 revised
minor
sync
some compressing
algorithm text

\Output{The status \safe or \unsafe, \rmcmt{and a counterexample if \unsafe.}}

@@

  \return (\unsafe,$\abs(\trail)$)}

@@

abstract transformers $\abstransset$ w.r.t.\ an abstract domain~$\domain$.  
The algorithm is parametrised by propagation \rmcmt{$(\propheur)$}, decision

@@

transformers $\abstrans\in\abstransset$ that were used to

@@

\rmcmt{a decision is added to the trail only if it refines the trail.}

@@

\rmcmt{to mark it as a decision.}

@@

The procedure $\deduce$ is called next to infer new meet irreducibles
taking into account the current decision.  The model search phase
alternates between the decision and deduction until $\deduce$ returns
either \textsf{sat} or \textsf{conflict}.  In the former case, we have
found an abstract value that represents models of $\formula$, which
are counterexamples to the safety problem, and thus \rmcmt{we or ACDCL} return
\textsf{unsafe}.
%
% has found an abstract value that represents a set of models of $\formula$ or the
% deduction leads to a \textsf{conflict}.  Checking whether the abstract
% model concretises to a set of models of $\formula$; this
% corresponds to a $\gamma$-completeness~\cite{dhk2013-popl} check in
% abstract interpretation.  If $v$ is $\gamma$-complete, then it cannot
% be refined further.  Thus, the algorithm returns the abstract model
% $v$, which is a set of concrete models, and terminates with
% \textsf{unsafe} or the current abstraction is insufficient to
% determine the satisfiability of $\formula$.

In the latter case the algorithm enters in the $\analyzeconflict$
phase to learn the reason for the conflict.   There can be multiple
incomparable reasons for conflict.
% \pscmt{do you have to explain this here?} -- based on the choice of Unique
%Implication Point (UIP)~\cite{cdcl}.  
ACDCL heuristically chooses one reason $\conflictset$ and learns it 
by adding it as an abstract transformer to $\abstransset$. The algorithm 
backtracks by removing the content of $\trail$ up to a point where it does not 
conflict with $\conflictset$.  ACDCL then performs deductions with the learnt 
transformer.  If $\analyzeconflict$ returns $\false$ then no further
backtracking is possible.  Thus, the $\formula$ is unsatisfiable
and \rmcmt{we or ACDCL} return \textsf{safe}.

>>>>

\Output{The status \safe or \unsafe.}

@@

  \return (\unsafe)}

@@

abstract transformers $\abstransset$ w.r.t.\ an abstract domain~$\domain$. \pscmt{define} 
The algorithm is parametrised by propagation $(\propheur)$, decision

@@

transformers $\abstransel{}\in\abstransset$ that were used to

@@

%\rmcmt{a decision is added to the trail only if it refines the trail.}

@@

to mark it as a decision.

@@

The procedure $\deduce$ is called next to infer new meet irreducibles
taking into account the current decision.  The model search phase
alternates between the decision and deduction until $\deduce$ returns
either \textsf{sat} or \textsf{conflict}.  In the former case, we have
found an abstract value that represents models of $\formula$, which
are counterexamples to the safety problem, and thus ACDCL return
\textsf{unsafe}.
%
% has found an abstract value that represents a set of models of $\formula$ or the
% deduction leads to a \textsf{conflict}.  Checking whether the abstract
% model concretises to a set of models of $\formula$; this
% corresponds to a $\gamma$-completeness~\cite{dhk2013-popl} check in
% abstract interpretation.  If $v$ is $\gamma$-complete, then it cannot
% be refined further.  Thus, the algorithm returns the abstract model
% $v$, which is a set of concrete models, and terminates with
% \textsf{unsafe} or the current abstraction is insufficient to
% determine the satisfiability of $\formula$.

In the latter case the algorithm enters in the $\analyzeconflict$
phase to learn the reason for the conflict.   There can be multiple
incomparable reasons for conflict.
% \pscmt{do you have to explain this here?} -- based on the choice of Unique
%Implication Point (UIP)~\cite{cdcl}.  
ACDCL heuristically chooses one reason $\conflictset$ and learns it 
by adding it as an abstract transformer to $\abstransset$. The algorithm 
backtracks by removing the content of $\trail$ up to a point where it does not 
conflict with $\conflictset$.  ACDCL then performs deductions with the learnt 
transformer.  If $\analyzeconflict$ returns $\false$ then no further
backtracking is possible.  Thus, the $\formula$ is unsatisfiable
and ACDCL return \textsf{safe}.
